Making Sequential Programs Deterministic

### 2019-03-28 design.tex

In a type system,
a \textit{type} stands for a set of values.  It abstracts or restricts the
set of possible run-time values that an expression may evaluate to.
A programming language provides \emph{basetypes}, such as \<int>.
A \textit{type qualifier} on a \textit{type} adds additional constraints;
that is, it reduces the size of the set of values.
A type checker can verify the correctness of this \textit{type} with its dataflow analysis and subtyping rules.
In Java, a type qualifier is written as a type annotation with a leading \<@>, as in
\<@Positive int>.

>>>>

In a type system,
a \textit{type} represents a set of values.  It abstracts or restricts the
set of possible run-time values that an expression may evaluate to.
A programming language provides \emph{basetypes}, such as \<int>.
A \textit{type qualifier} on a \textit{type} adds additional constraints;
that is, it reduces the size of the set of values.
In Java, a type qualifier is written as a type annotation (which has a leading \<@>), as in
\<@Positive int>.
A type checker can verify the correctness of a \textit{type} via subtyping
rules and dataflow analysis.
